\documentclass{beamer}
\usetheme{boxes}
\usepackage{helvet}
\title{Rework -- The Secrets of 37signals}
\author{George Rogers}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}
\begin{frame}
  \frametitle{Outline}
  \begin{itemize}
  \item About 37signals.
  \item Embrace Constraints
  \item Start @ The Epicenter
  \item Launch Now
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{About 37signals}
  Products
  \begin{itemize}
  \item Basecamp -- A Project Manager and Their First Product.
  \item Highrise -- A Contact Manager
  \item Campfire -- A Corporate Chat Service.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Embrace Constraints}
  \begin{itemize}
  \item Limited resources force you to be creative.
  \item Writers use constraints to force creativity all the time.
    \begin{itemize}
    \item Shakespeare used the constraints of sonnets to force creativity.
    \end{itemize}
  \item When 37signals started base camp they had some serious constraints\ldots
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Constraints of 37signals when building Basecamp}
  \begin{itemize}
  \item Lack of locality
    \begin{itemize}
    \item David Heinemier Hansson was working in Denmark.
    \item The rest of the team was working in the States.
    \end{itemize}
  \item No outside money.
  \item A small team.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Start @ The Epicenter}
  \begin{enumerate}
  \item The Epicenter
  \item The Next Most Important Thing
  \item Everything else
  \end{enumerate}
\end{frame}
\begin{frame}
  \frametitle{Duh?}
  \begin{itemize}
  \item Unfortunately most people start at the perifery
    when designing documents and interfaces\ldots
  \item So they don't spend time on the most important part.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Launch Now}
  \begin{itemize}
  \item Launch it if you are missing features.
  \item Launch as soon as posible so you can see what realy is important.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Result}
  \begin{itemize}
  \item A very profitable company that produces a great product
  \end{itemize}
\end{frame}
\end{document}
